### 2017-05-22 R/NHTS.Rmd
Created TravelSurvey Rmd
I am breaking ITHIM.Rmd into smaller pieces that can be managed with the TravelSurvey class

#### Create a handful of functions to help parse data

@@

NHTS.trips <- with(DAYV2PUB,{
    data.frame(HOUSEID = HOUSEID,
                   PERSONID = PERSONID,
                   TDCASEID = TDCASEID,
                   AT = ifelse(TRPTRANS == "22", "cycle",
                        ifelse(TRPTRANS == "23", "walk",
                        ifelse(!is.na(TRPTRANS), "other", NA))),
                   TRVL_MIN = as.numeric(TRVL_MIN),
                   #TRVLCMIN = as.numeric(TRVLCMIN),
                   URBRUR  = as.factor(URBRUR),
                   MSACAT = as.factor(MSACAT),
                   MSA = ifelse(MSASIZE %in% 1:5, TRUE, FALSE),
                   TRPTRANS = as.factor(TRPTRANS),
                   TRPMILES = as.numeric(TRPMILES)
)})

@@

#### Subset and Merge

We now correct for zero trip times in NHTS.

```{r subset, eval = compute, fig.width = 10, echo = FALSE}

NHTS.person <- subset( NHTS.person, MSA == TRUE )
NHTS.trips <- subset(NHTS.trips, !is.na(TRVL_MIN))

NHTS <- merge(NHTS.person, NHTS.trips, by = c("HOUSEID","PERSONID"), all.x = TRUE)
NHTS <- within(NHTS, TRVL_MIN <- ifelse(is.na(TRVL_MIN), 0, TRVL_MIN))
saveRDS(NHTS, file = "./data/NHTS.rds")

```{r msaMatrix, eval = compute, fig.width = 10, echo = FALSE}
msaMatrix <- matrix(c(5602,4472,1922,7320,3120,6200,3362,7362,5720,4992,8872,
8280,7240,0640,6922,5960,3600,0520,8960,3480,1602,6840,
1280,1520,5360,6640,1122,5082,6162,2162,4920,7602,6480,
5120,1692,7040,7160,6442,4120,4520,6280,2082,1642,3760,
3280,1840,5880,3000,5560,
"NY/NJ Metro","Los Angeles-Riverside-Orange County","Dallas-Fort Worth","San Diego","Greensboro-Winston Salem", "Phoenix/Mesa","Houston-Galveston-Brazoria", "San Francisco-Oakland-San Jose", "Norfolk-Virginia Beach", "Miami-Ft. Lauderdale", "Washington-Baltimore", rep("no label yet", 38)), ncol = 2)
```

@@

person.df <- with(NHTS.person,{
    data.frame(houseID=HOUSEID, subjectID=PERSONID, sex = SEX, age = AGE, location = HHS)
    })

@@

NHTS.TravelSurvey <- new("TravelSurvey", person = person.df, trip = trip.df)
saveRDS(NHTS.TravelSurvey, file = "~/GHI/R/data/NHTS.TravelSurvey.rds")

@@

>>>>

@@

NHTS.trips <- with(DAYV2PUB,{
    data.frame(HOUSEID = HOUSEID,
                   PERSONID = PERSONID,
                   TDCASEID = TDCASEID,
                   AT = ifelse(TRPTRANS == "22", "cycle",
                        ifelse(TRPTRANS == "23", "walk",
                        ifelse(!is.na(TRPTRANS), "other", NA))),
                   TRVL_MIN = as.numeric(TRVL_MIN),
                   URBRUR  = as.factor(URBRUR),
                   MSACAT = as.factor(MSACAT),
                   MSA = ifelse(MSASIZE %in% 1:5, TRUE, FALSE),
                   TRPTRANS = as.factor(TRPTRANS),
                   TRPMILES = as.numeric(TRPMILES)
)})

@@

#### Create TravelSurvey Object

@@

person.df <- with(NHTS.person,{
    data.frame(houseID=HOUSEID, subjectID=PERSONID, sex = SEX, age = AGE, location = MSA_ID)
    })

@@

NHTS.TravelSurvey <- new("TravelSurvey", person = person.df, trip = trip.df)

saveRDS(NHTS.TravelSurvey, file = "~/GHI/R/data/NHTS.TravelSurvey.rds")
```

```{r TravelSurvey2, eval = compute, fig.width = 10, echo = FALSE}
NHTS.TravelSurvey <- readRDS(file = "~/GHI/R/data/NHTS.TravelSurvey.rds")

@@

```{r msaMatrix, eval = FALSE, fig.width = 10, echo = FALSE}
msaMatrix <- matrix(c(5602,4472,1922,7320,3120,6200,3362,7362,5720,4992,8872,
8280,7240,0640,6922,5960,3600,0520,8960,3480,1602,6840,
1280,1520,5360,6640,1122,5082,6162,2162,4920,7602,6480,
5120,1692,7040,7160,6442,4120,4520,6280,2082,1642,3760,
3280,1840,5880,3000,5560,
"NY/NJ Metro","Los Angeles-Riverside-Orange County","Dallas-Fort Worth","San Diego","Greensboro-Winston Salem", "Phoenix/Mesa","Houston-Galveston-Brazoria", "San Francisco-Oakland-San Jose", "Norfolk-Virginia Beach", "Miami-Ft. Lauderdale", "Washington-Baltimore", rep("no label yet", 38)), ncol = 2)
```

```{r foob, eval = FALSE, echo = FALSE}
#NHTS.person <- subset( NHTS.person, MSA == TRUE )
#NHTS.trips <- subset(NHTS.trips, !is.na(TRVL_MIN))

#NHTS <- merge(NHTS.person, NHTS.trips, by = c("HOUSEID","PERSONID"), all.x = TRUE)
#NHTS <- within(NHTS, TRVL_MIN <- ifelse(is.na(TRVL_MIN), 0, TRVL_MIN))
#saveRDS(NHTS, file = "./data/NHTS.rds")
```
